\thesistitle

### 2025-07-26 manuscript/main.tex
adress footer

%=== Layout and typography ===
\usepackage{caption}
\usepackage{multicol}
\usepackage{microtype}
\usepackage{titlesec}
\titleformat{\chapter}[hang]{\normalfont\huge\bfseries}{}{0pt}{}
\titlespacing*{\chapter}{0pt}{1.5em}{1em}
% Prevent chapters from starting on a new page
\usepackage{etoolbox}
\makeatletter
  % In the standard report class \chapter does:
  %    \if@openright \cleardoublepage \else \clearpage \fi
  % so we remove that entire conditional.
  \patchcmd{\chapter}
    {\if@openright\cleardoublepage\else\clearpage\fi}
    {}
    {}{}

@@

%=== File Metadata ======
\begin{filecontents*}[overwrite]{\jobname.xmpdata}
\Author{\authorname}
\Title{\thesistitle}
\Language{de-AT}
\Keywords{a\sep list\sep of\sep keywords}
\Publisher{TU Wien}
\Subject{Thesis}
\end{filecontents*}

@@

%—— German Title Page ——
\begin{titlepage}
  % Top‑left TU Wien logo
  \noindent
  \includegraphics[width=0.3\textwidth]{graphics/tuWienLogo.png}

@@

%—— English Title Page ——
\begin{titlepage}
  % Top‑left TU Wien logo
  \noindent
  \includegraphics[width=0.3\textwidth]{graphics/tuWienLogo.png}

>>>>

%=== Layout and typography ===
\usepackage{caption}
\usepackage{multicol}
\usepackage{microtype}
\usepackage{fancyhdr}
\fancypagestyle{titlepage}{%
  \fancyhf{}                        % clear all header and footer fields
  \renewcommand{\headrulewidth}{0pt} % no rule in the header
  \renewcommand{\footrulewidth}{0.4pt}% draw a rule above the footer
  \fancyfoot[C]{\small
    Technische Universität Wien\\
    A-1040 Wien Karlsplatz 13 \quad Tel.\ +43-1-58801-0 \quad www.tuwien.at
  }
}
\usepackage{titlesec}
\titleformat{\chapter}[hang]{\normalfont\huge\bfseries}{}{0pt}{}
\titlespacing*{\chapter}{0pt}{1.5em}{1em}
% Prevent chapters from starting on a new page
\usepackage{etoolbox}
\makeatletter
  % In the standard report class \chapter does:
  %    \if@openright \cleardoublepage \else \clearpage \fi
  % so we remove that entire conditional.
  \patchcmd{\chapter}
    {\if@openright\cleardoublepage\else\clearpage\fi}
    {}
    {}{}

@@

%=== File Metadata ======
\begin{filecontents*}[overwrite]{\jobname.xmpdata}
\Author{\authorname}
\Title{\thesistitle}
\Language{de-AT}
\Keywords{VS Code extension\sep Langium\sep Languages\sep Language tooling}
\Publisher{TU Wien}
\Subject{Thesis}
\end{filecontents*}

@@

%—— German Title Page ——
\begin{titlepage}
  \thispagestyle{titlepage}
  % Top‑left TU Wien logo
  \noindent
  \includegraphics[width=0.4\textwidth]{graphics/tuWienLogo.png}

@@

%—— English Title Page ——
\begin{titlepage}
  \thispagestyle{titlepage}
  % Top‑left TU Wien logo
  \noindent
  \includegraphics[width=0.4\textwidth]{graphics/tuWienLogo.png}
